MaxEnt: What is it good for?

### 2015-06-17 ms.tex
Plots
gotta think about notation

We start with a {\it hypothesis space} of mutually exclusive and
exhaustive propositions $\{A_1, A_2, ..., A_N\}$ which we will sometimes
describe as possible values $\{x_1, x_2, ..., x_N\}$ of an unknown variable $x$.
On the basis of background
information $I$ (hereafter suppressed), we know that one and only one of these
propositions is true, but we don't know which. We model states of
uncertainty by probability distributions over the hypothesis space,
such as $\{p_i\}_{i=1}^N$ where $P(A_i) = p_i$ is the probability of $A_i$.
Of course all of the $p_i$ must be non-negative and their sum must be 1.
From this probability distribution, various probabilities can be derived
using the sum and product rules. For example, the probability of
($A_4$ {\bf or} $A_5$) is $p_4 + p_5$, and the probability of $A_5$ given
($A_5$ {\bf or} $A_6$) is $p_5/(p_5 + p_6)$. The rules of probability must
be obeyed if the rules for combining are to remain consistent
with the symmetries of logical {\bf and} and {\bf or}
\citep{2010arXiv1008.4831K}.

Relative entropy
\begin{eqnarray}
H(\boldsymbol{p}; \boldsymbol{q}) &=& -\sum_i p_i \log\left(\frac{p_i}{q_i}\right) 
\end{eqnarray}

>>>>

\section{Probability}
We start with a {\it hypothesis space} of mutually exclusive and
exhaustive propositions $\{A_1, A_2, ..., A_N\}$ which we will usually
think of as possible values of an unknown quantity $x$.
On the basis of background
information $I$ (hereafter suppressed), we know that one and only one of these
propositions is true (i.e. the true value of $x$ is in our set),
but we don't know which. We model states of
uncertainty by probability distributions over the hypothesis space,
such as $\{p_i\}_{i=1}^N$ where $P(A_i) = p_i$ is the probability of $A_i$.
The standard loose Bayesian notation would write this distribution simply
as $p(x)$.

Of course all of the $p_i$ must be non-negative and their sum must be 1.
From this probability distribution, various probabilities can be derived
using the sum and product rules. For example, the probability of
($A_4$ {\bf or} $A_5$) is $p_4 + p_5$, and the probability of $A_5$ given
($A_5$ {\bf or} $A_8$) is $p_5/(p_5 + p_8)$. The rules of probability must
be obeyed if the rules for combining are to remain consistent
with the symmetries of logical {\bf and} and {\bf or}
\citep{2010arXiv1008.4831K}.

\begin{figure}
\begin{center}
\includegraphics[scale=0.5]{distribution.pdf}
\caption{\label{fig:distribution}}
\end{center}
\end{figure}

Relative entropy
\begin{eqnarray}
H(p; q) &=& -\sum_i p_i \log\left(\frac{p_i}{q_i}\right) 
\end{eqnarray}
